\documentclass[11pt,letterpaper,notitlepage,onesided]{nwh_hw}
\usepackage{graphicx,color,amsmath,amssymb}
%\usepackage{amssymb}
%\usepackage{wasysym}
\usepackage[dvips]{epsfig}
\usepackage[pdftex,
colorlinks,linkcolor={blue},citecolor={blue},
urlcolor={blue}
]{hyperref}


\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\topmargin}{-0.25in} 
\setlength{\headheight}{0.15in}
\setlength{\headsep}{0.5in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}
\setlength{\hoffset}{0in}

\setlength{\parindent}{0in}
\setlength{\parskip}{2ex}

%\pagestyle{myheadings}
%\pagestyle{fancy}

\markright{ASTR 5550 ---  Spring 2012}


% For figures:
\usepackage{graphicx}

\begin{document}

\input{mymacros}

%\maketitle
\pagestyle{myheadings}

\section*{Homework 1}

Due Friday, 27 Jan, at the beginning of class. 

%I'll choose one person at random to demonstrate in class, using my
%computer, how to generate an array of random numbers, plot, and
%histogram them as in Section~\ref{sec:idlskills} below. Be prepared to
%do this.

Reading Assignment: Read Wall \& Jenkins, Chapters 1 \& 2. Optional
additional reading: For an excellent in-depth discussion of Bayesian
vs. Frequentist methods, see Loredo, ``From Laplace to Supernova SN
1987A: Bayesian Inference in Astrophysics,'' 1990, posted under the
``papers'' link on the course homepage.


\section{A Hunt for Galaxy Clusters}

An astronomer is hunting for a new galaxy cluster to study. She knows
from previous surveys of a different part of the sky that the
probability of finding a galaxy cluster is 30\% in a single
square-degree image (the field of view of her instrument). The
astronomer's plan is to take images until she finds a single cluster,
then stop.

a) Find an expression for the probability $P[k]$ of the astronomer
finding the first cluster (and stopping) after the $k^\mathrm{th}$
image is taken.

b) Show that, in your solution from a), $\Sigma_{k=1}^{\infty} P[k] = 1$

c) Write a simulation of the astronomer's observations in Python/IDL/Matlab,
run $N=1000$ trials of her observing scheme, and plot a histogram of
frequency vs. number of images $k$ taken in a given trial. For
comparison purposes, on your histogram, overplot your analytical
solution for $P[k]$ from a), multiplying by a factor of 1000 to
account for the fact that you have generated $N=1000$ trials. Does
your histogram agree with your analytical calculation?


\section{Bayesian Analysis of Tainted Beef Patties}

Two differernt suppliers, $A$ and $B$, provide a supermarket with
ground beef patties.  In the past, 0.01\% of the patties supplied by
$A$ and 0.03\% of the patties supplied by $B$ have been found to be
contaminated by E.\ Coli. $A$ supplies five times as many patties to
the supermarket as $B$. 

An unsuspecting consumer is found to be infected by E.\ Coli due to
eating a burger purchased at this supermarket. Using Baye's Theorem,
what is the probability that the contaminated burger was supplied by
$A$?


\section{PDF, CDF, and Moments}

Consider the following probability density function (PDF): 

\[ 
f (x) = \begin{cases}
  x e^{-x} &  x \geq 0, \\
  0 & x < 0.
\end{cases}
\]

a) Plot the PDF, and verify that $\int_{-\infty}^\infty f(x) dx = 1$.

b) Find the cumulative distribution function (CDF), $F(x)$.

c) Find the mean, $\mu \equiv \exn{x} $ of the distribution. What fraction of the total probability lies below the mean? 

d) Find the variance $\sigma^2 \equiv \var{x}$ of the distribution. What fraction of the total probability lies within the interval $\mu \pm \sigma$, where $\sigma = \sqrt{\sigma^2}$ is the standard deviation? 



\end{document}
